---
title: "Course Project: Shiny Application and Reproducible Pitch. @mmblanes"
author: "Manuel Martínez Blanes"
date: "27 de noviembre de 2016"
output: ioslides_presentation
---

## Introduction
The dataset used here represents the evolution of narcotic drugs in certain European pharmacies.
Data, source code for ui.R and server.R files are available on the GitHub repo: https://github.com/mmblanes/Course-Project--Shiny-Application-and-Reproducible-Pitch 

This is my work for the course Developing Data Products.

The app is avalilable at: https://mmblanes.shinyapps.io/EjmploDeShiny/

## Funcionality
The app provide a tool for to analisys the request of narcotics drug at Spain (at last 6 months).

First, you must choose the variable of interest:Generados (requested), Entregados (deliveres),or Cancelados (canceled)

Second, you can choose your the correspodient tab to show the plot or the summary.

## Plot
```{r, message=FALSE}
setwd("~/EjmploDeShiny")
datos<-read.csv(file="estupe.csv",head=TRUE,sep=";")
hist(datos$TotalVales, main=paste('Variable: Generados ', sep=''))
```

## Dataset
```{r}
str(datos)
```

